\begin{Summary}{Plagiarism Declaration}
	I have read and understand the Stellenbosch University Policy on Plagiarism and the definitions of plagiarism and self-plagiarism contained in the Policy [Plagiarism: The use of the ideas or material of others without acknowledgement, or the re-use of one's own previously evaluated or published material without acknowledgement or indication thereof (self-plagiarism or text-recycling)].\par
	\vspace{0.4cm}
	I also understand that direct translations are plagiarism, unless accompanied by an appropriate acknowledgement of the source. I also know that verbatim copy that has not been explicitly indicated as such, is plagiarism.\par
	\vspace{0.4cm}
	I know that plagiarism is a punishable offence and may be referred to the University's Central Disciplinary Committee (CDC) who has the authority to expel me for such an offence.\par
	\vspace{0.4cm}
	I know that plagiarism is harmful for the academic environment and that it has a negative impact on any profession.\par
	\vspace{0.4cm}
	Accordingly all quotations and contributions from any source whatsoever (including the internet) have been cited fully (acknowledged); further, all verbatim copies have been expressly indicated as such (e.g. through quotation marks) and the sources are cited fully.\par
	\vspace{0.4cm}
	I declare that, except where a source has been cited, the work contained in this assignment is my own work and that I have not previously (in its entirety or in part) submitted it for grading in this module/assignment or another module/assignment.\par
	\vspace{0.4cm}
	I declare that have not allowed, and will not allow, anyone to use my work (in paper, graphics, electronic, verbal or any other format) with the intention of passing it off as his/her own work. \par
	\vspace{0.4cm}
	I know that a mark of zero may be awarded to assignments with plagiarism and also that no opportunity be given to submit an improved assignment.\par
	\vspace{2cm} 
	
	
	\noindent%
	\parbox{.5\textwidth}{%
		Signature:\quad\dotfill\par
		\hfill L.E.V.\ Kingwill \hspace{1.2cm}\null\par
		\hfill 20725728 \hspace{1.2cm}\null}
	
	
	\vspace{1cm}
	\noindent%
	\parbox{.5\textwidth}{%
		Date:\quad\dotfill\par}
\end{Summary}